\section{Computer Recommendations}
Charleston Southern University provides computer labs where students work on computer science projects. Therefore, a personal computer is not required for in-person students; however, most students prefer having a personal computer for convenience, especially after their first semester.

\vspace{1em}
You may choose a Mac or a PC, but we recommend PCs for more customization in hardware and software. You're free to select any brand, but we recommend the following specifications:

\begin{itemize}
    \item
        \textbf{CPU}: Intel or AMD CPU with at least 6 cores. Choose models within the last few generations, such as:
        \begin{itemize}
            \item Intel 13\textsuperscript{th} gen or newer
            \item AMD Ryzen 7000 series or newer
            \item Apple M3 or newer if purchasing a MacBook.
        \end{itemize}
    \item
        \textbf{Memory}: A minimum of 16 GB of RAM\@. 32 GB is recommend.
    \item
        \textbf{Storage}: A solid-state hard drive (SSD) with a capacity of 500 GB or more.
    \item
        \textbf{I/O}: Ethernet and HDMI ports. Alternatively, you may purchase a USB dongle that provides these ports.
    \item
        \textbf{Graphics}: A dedicated graphics card is \emph{not} required for your needs.
    \item
        \textbf{Operating System}:
        \begin{itemize}
            \item {Mac}: Upgrade to the latest version of macOS\@. In more advanced courses, you may need to also purchase \href{https://www.parallels.com/products/desktop/}{Parallels Desktop} or a similar virtual machine software.
            \item {PC}: Windows 11 or your choice of Linux distribution.
        \end{itemize}
\end{itemize}