\phantomsection\addcontentsline{toc}{section}{BA in Applied Computing with a Cybersecurity Concentration}%
\section*{Bachelor of Arts: Applied Computing\\with a Cybersecurity Concentration}

\begin{reqgroup}{Liberal Arts Core Requirements (48--49 hours)}
%\subsection*{}
\begin{checklist}
\begin{minipage}[t]{0.5\linewidth}
	\item (3) English 111
	\item (3) English 112
	\item (3) English 202, 203 or 204
	\item (3) COMM 110 Public Speaking
	\item (3) Any 3-hour foreign language course
	\item (4) \textbf{CSCI 235  Procedural Programming}
	\item (3) CHST 111  Survey of the Old Testament
	\item (3) CHST 112  Survey of the New Testament
	\item (3) History 111, 112 or 113 Western Civ.
\end{minipage}
\begin{minipage}[t]{0.5\linewidth}
	\item (3)	Another History, POLI 201, or CHIST 140
	\item (3)	ART 202 Art Appr, or MUSI 171 or 371, or THEA 218 or 311
	\item (3)	\textbf{CRIM 210 Introduction to Criminal Justice}
	\item (3--4)	\textbf{Math 110 or 111 College Algebra}
	\item (4)	 Lab Science
	\item (4)	 Lab Science\\Limited one lab science course per category of Biology, Chemistry,
Geology, or Physics.
\end{minipage}
\end{checklist}
\end{reqgroup}

%\vspace{1em}

\begin{reqgroup}{Core Major Studies (26 hours)}
\begin{checklist}
\begin{minipage}{0.5\linewidth}
	\item (4) CSCI 301	Survey of Scripting Languages
	\item (4) CSCI 315	Data Structure Analysis
	\item (4) CSCI 325	Object-Oriented Programming
	\item (4) CSCI 332	Applied Networking
\end{minipage}
\begin{minipage}{0.5\linewidth}
	\item (4) CSCI 419	Database Management
	\item (4) CSCI 490	Computer Science Exit Exam
	\item (4) CSCI 495	Systems Analysis and Software Design
	\item (4) MATH 213	Probability and Statistics
	\end{minipage}
\end{checklist}
\end{reqgroup}

\begin{reqgroup}{Cybersecurity Concentration (40 hours)}
\begin{center}%
(This concentration can be completed completely online.)\vspace{-0.5em}%
\end{center}%
\begin{checklist}
\begin{minipage}[t]{0.5\linewidth}
	\item (4) CSCI 352 Cyber Defense
	\item (3) CSCI 405 Principles of Cybersecurity
	\item (4) CSCI 433 Network Security
	\item (0) CSCI 496 Senior Portfolio Review
\end{minipage}
\begin{minipage}[t]{0.5\linewidth}
	\item (1) CSCI 497 Senior Project Design
	\item (1) CSCI 498 Senior Project Construction
	\item (1) CSCI 499 Senior Project Implementation/Defense
	\item (3) CRIM 227 Critical Thinking/Writing in Criminal Justice
\end{minipage}
\end{checklist}

\tcblower

An additional 23 hours may come from any courses at the 300 level or above from the following categories:\\CRIM (including 212, 232, and 255), CSCI, and MATH.
\begin{checklist}
\begin{minipage}[t]{0.5\linewidth}
	\blankReq
	\blankReq
	\blankReq
	\blankReq
\end{minipage}
\begin{minipage}[t]{0.5\linewidth}
	\blankReq
	\blankReq
	\blankReq
	\blankReq
\end{minipage}
\end{checklist}
\end{reqgroup}

\begin{reqgroup}{General Electives (11 hours)}
Any 11 hours can be taken; however, the following are suggested or may be required as prerequisites.
\begin{checklist}
\begin{minipage}[t]{\linewidth}
	\item (1)	GNED 101	First-Year Seminar
	\item (3--4)	CSCI 217	Practical Programming and Problem Solving or CSCI 215	Programming in Alice\\
	\begin{minipage}[t]{0.5\linewidth}
		\blankReq
	\end{minipage}
	\begin{minipage}[t]{0.5\linewidth}
		\blankReq
	\end{minipage}
\end{minipage}
\end{checklist}
\end{reqgroup}

Notes:%
\begin{enumerate}\footnotesize
	\item This major does not require a minor.
	\item Prior to entry into the senior project series, student must submit a portfolio for review. See CSCI 496 in catalog for detail.
	\item For completion is four years, students must begin cognate requirements in the freshman year. If prerequisites are needed for cognate requirements, summer courses may be required to move into the proper scheduling cycle.
	\item Graduates must meet residency requirements. 36 of the last 46 hours must be earned while attending CSU. Of these, at least 12 must be 300-400 level courses.
	\item Students may request one official degree audit through their MyCSU account, which is recommended during the next to last semester.
	\item Students are responsible for applying to graduate. See the Registrar.
	\item Full-time day students must meet chapel requirements. See the Student Development section of the catalog.
	\item In cases of conflict between this checklist and the catalog, the catalog takes precedence.
\end{enumerate}
