\phantomsection\addcontentsline{toc}{section}{BS in Cybersecurity}%
\section*{Bachelor of Science: Cybersecurity}

\begin{reqgroup}{Liberal Arts Core Requirements (49 hours)}
%\subsection*{}
\begin{checklist}
\begin{minipage}[t]{0.5\linewidth}
	\item (3) ENGL 111 or 180 Composition and Rhetoric *
	\item (3) ENGL 112 Composition with Intro\@. to Literature *
	\item (3) English 202, 203, or 204 Literature
	\item (3) COMM 110 Public Speaking
	\item (3) Any 3-hour foreign language course
	\item (4) \textbf{CSCI 235  Procedural Programming} *
	\item (3) CHST 111  Survey of the Old Testament
	\item (3) CHST 112  Survey of the New Testament
	\item (3) HIST 111, 112, or 113 Western Civ.
\end{minipage}
\begin{minipage}[t]{0.5\linewidth}
	\item (3) Another History, POLI 201, or CHST 140
	\item (3) ART 202 Art Appr, or MUSI 171 or 371, or THEA 218 or 311
	\item (3) \textbf{CRIM 210 Introduction to Criminal Justice}
	\item (4) \textbf{MATH 221 Calculus I}
	\item (4) Lab Science
	\item (4) Lab Science\\Limited one lab science course per category of Biology, Chemistry,
Geology, or Physics.
\end{minipage}
\end{checklist}
\end{reqgroup}

%\vspace{1em}

\begin{reqgroup}{Computer Science/Mathematics Requirements (52 hours)}
\begin{checklist}
\begin{minipage}[t]{0.5\linewidth}
	\item (3) MATH 213 Probability and Statistics
	\item (3) MATH 330 Discrete Mathematics
	\item (4) CSCI 301 Survey of Scripting Languages
	\item (4) CSCI 325 Object-Oriented Programming
	\item (4) CSCI 330 Computer Architecture
	\item (4) CSCI 332 Applied Networking
	\item (4) CSCI 352 Cyber Defense
	\item (3) CSCI 405 Principles of Cybersecurity
	\item (4) CSCI 433 Network Security
	\item (4) CSCI 452 Network Penetration Testing and\\Ethical Hacking
\end{minipage}
\begin{minipage}[t]{0.5\linewidth}
	\item (0) CSCI 491 Cybersecurity Exit Exam
	\item (0) CSCI 496 Senior Portfolio Review
	\item (1) CSCI 497 Senior Project Design
	\item (1) CSCI 498 Senior Project Construction
	\item (1) CSCI 499 Senior Project Implementation/Defense
	\item (12) Elective CSCI hours from: CSCI 315 Data Structures;
	\item \hspace{1em} CSCI 419 Database Management; CSCI 409 Mobile App
	\item \hspace{1em} Development; CSCI 434 Data Mining, CSCI 316
	\item[] \hspace{1em} Competitive Security, or other 300/400 CSCI course


\end{minipage}
\end{checklist}
\end{reqgroup}

\begin{reqgroup}{Criminal Justice Requirements (9 hours)}
\begin{checklist}
\begin{minipage}[t]{0.5\linewidth}
	\item (3) CRIM 212 - Techniques of Criminal Investigations
\end{minipage}
\begin{minipage}[t]{0.5\linewidth}
	\item (3) Criminal Justice electives at the 200 level or higher
	\item (3) Criminal Justice electives at the 200 level or higher
\end{minipage}
\end{checklist}
Recommended courses include CRIM 232 Current Issues and Trends in Criminal Justice,
CRIM 455 Homeland Security, and CRIM 312 Advanced Criminal Justice Techniques
\end{reqgroup}

\begin{reqgroup}{General Electives (10 hours)}
Any 10 hours can be taken; however, the following are suggested or may be required as prerequisites.
\begin{checklist}
\begin{minipage}[t]{\linewidth}
	\item (1)	GNED 101	First-Year Seminar
	\item (3--4)	CSCI 217	Practical Programming and Problem Solving or CSCI 215	Programming in Alice
	\item (3--4) Math 110 or 111 College Algebra
	\item (4) MATH 130 Precalculus
	\item (4) MATH 222 Calculus II \em{Recommended for students considering employment in the federal government.}
\end{minipage}
\end{checklist}
\end{reqgroup}

Notes:%
\begin{enumerate}\footnotesize
	\item This major is
		\href{https://www.abet.org/accreditation/what-is-accreditation/why-abet-accreditation-matters/}{accreddited by the Computing Accreditation Commission of ABET}.
	\item This major does not require a minor.
	\item * Indicates courses that must be completed within the first four major terms (Fall and Spring).
	\item If prerequisites are needed for the cognate requirements, summer courses may be required for four-years completion.
	\item Residency requirement: 36 of the last 46 hours must be earned while attending CSU. Of these, at least 12 must be 300--400 level courses.
	\item Students may request one official degree audit through their \href{https://portal.csuniv.edu/}{MyCSU account}, which is recommended during the next to last semester.
	\item Students are responsible for applying to graduate. See the Registrar.
	\item Full-time day students must meet chapel requirements. See the Student Development section of the catalog.
	\item In cases of conflict between this checklist and the catalog, the catalog takes precedence.
\end{enumerate}