\phantomsection\addcontentsline{toc}{section}{BS in Computer Science}%
\section*{Bachelor of Science: Computer Science}

\begin{reqgroup}{Liberal Arts Core Requirements (49 hours)}
%\subsection*{}
\begin{checklist}
\begin{minipage}[t]{0.5\linewidth}
	\item (3) English 111 *
	\item (3) English 112 *
	\item (3) English 202, 203 or 204
	\item (3) COMM 110 Public Speaking
	\item (3) Any 3-hour foreign language course
	\item (4) \textbf{CSCI 235  Procedural Programming} *
	\item (3) CHST 111  Survey of the Old Testament
	\item (3) CHST 112  Survey of the New Testament
	\item (3) History 111, 112 or 113 Western Civ.
\end{minipage}
\begin{minipage}[t]{0.5\linewidth}
	\item (3)	Another History, POLI 201, or CHIST 140
	\item (3)	ART 202 Art Appr, or MUSI 171 or 371, or THEA 218 or 311
	\item (3)	BUSI 203, CRIM 210, ECON 211, ECON 212, HEAL 201, POLI 101, PSYC 110, or SOCI 101, 203, or 205
	\item (4)	\textbf{MATH 221 Calculus I} *
	\item (4)	 Lab Science
	\item (4)	 Lab Science\\Limited one lab science course per category of Biology, Chemistry,
Geology, or Physics.
\end{minipage}
\end{checklist}
\end{reqgroup}

%\vspace{1em}

\begin{reqgroup}{Computer Science/Mathematics Requirements (60--63 hours)}
\begin{checklist}
\begin{minipage}[t]{0.5\linewidth}
	\item (3) MATH 213 Probability and Statistics\\or MATH 346 (3) \& MATH 347 (3)
	\item (4) MATH 222 Calculus II
	\item (4) MATH 321 Calculus III\\or MATH 326 Linear Algebra
	\item (4) MATH 330 Discrete Mathematics

	\item (4) CSCI 301 Survey of Scripting Languages
	\item (4) CSCI 315 Data Structure Analysis
	\item (4) CSCI 325 Object-Oriented Programming
	\item (4) CSCI 330 Computer Architecture
	\item (4) CSCI 332 Applied Networking
	\item (4) CSCI 415 Algorithms
	\item (4) CSCI 419 Database Management


\end{minipage}
\begin{minipage}[t]{0.5\linewidth}
	\item (4) CSCI 431 Operating Systems
	\item (0) CSCI 490 Computer Science Exit Exam
	\item (3) CSCI 495 Systems Analysis and Software Design
	\item (0) CSCI 496 Senior Portfolio Review
	\item (1) CSCI 497 Senior Project Design
	\item (1) CSCI 498 Senior Project Construction
	\item (1) CSCI 499 Senior Project Implementation/Defense

	\item (8) Eight Elective CSCI hours from:
	\item \hspace{1em}\begin{minipage}[t]{\dimexpr\linewidth-1em\relax}CSCI 322 Multimedia (4); 334 User-Interface (4); 360 Mobile App Dev.; 409 Artfcl Intl (4); 432 Mobile/Wireless Ntwk (4); 433 Ntwk Security(4); 434 Human-Comp. Inter. (4); 435 Adv. Ntwk (4); 442 Data Mining (4); 450 Graphics (4); 452 Net. Pen., Test., \& Ethical Hacking (4); or other approved CSCI elective at 300/400 level\end{minipage}


\end{minipage}
\end{checklist}
\end{reqgroup}

\begin{reqgroup}{General Electives (16 hours)}
Any 16 hours can be taken; however, the following are suggested or may be required as prerequisites.
\begin{checklist}
\begin{minipage}[t]{\linewidth}
	\item (1)	GNED 101	First-Year Seminar
	\item (3--4)	CSCI 217	Practical Programming and Problem Solving or CSCI 215	Programming in Alice
	\item (3--4) Math 110 or 111 College Algebra
	\item (4) MATH 130 Precalculus
	\blankReq
\end{minipage}
\end{checklist}
\end{reqgroup}

Notes:%
\begin{enumerate}\footnotesize
	\item This major is
		\href{https://www.abet.org/accreditation/what-is-accreditation/why-abet-accreditation-matters/}{accreddited by the Computing Accreditation Commission of ABET}.
	\item This major does not require a minor.
	\item * Indicates courses that must be completed within the first four major terms (Fall and Spring).
	\item If prerequisites are needed for the cognate requirements, summer courses may be required for four-years completion.
	\item Graduates must meet residency requirements. 36 of the last 46 hours must be earned while attending CSU. Of these, at least 12 must be 300-400 level courses.
	\item Students may request one official degree audit through their \href{https://portal.csuniv.edu/}{MyCSU account}, which is recommended during the next to last semester.
	\item Students are responsible for applying to graduate. See the Registrar.
	\item Full-time day students must meet chapel requirements. See the Student Development section of the catalog.
	\item In cases of conflict between this checklist and the catalog, the catalog takes precedence.
\end{enumerate}