\phantomsection\addcontentsline{toc}{section}{Minor in Applied Computing}%
\section*{Minor in Applied Computing}

\begin{reqgroup}{Core Courses Required for All Tracks (7--8 hours)}
\begin{checklist}
\begin{minipage}[t]{0.5\linewidth}
	\item (3--4) CSCI 215 Programming in Alice or CSCI 217 Practical Programming and Problem Solving
	\item (4) CSCI 235	Procedural Programming
\end{minipage}
\begin{minipage}[t]{0.5\linewidth}
\end{minipage}
\end{checklist}
\end{reqgroup}

\vspace{1em}
\subsection*{Choose one of the following tracks}

\begin{reqgroup}{Computer Programming Track (11--12 hours)}
\begin{checklist}
	\item (4) CSCI 332 Applied Networking
	\item (4) CSCI 325 Object-Oriented Programming
	\item (3--4) Any 300/400 level CSCI course that does not duplicate a course in the major.
\end{checklist}
\end{reqgroup}

\begin{reqgroup}{Cybersecurity Track (11 hours)}
\begin{checklist}
	\item (4) CSCI/CRIM 405 Principles of Cybersecurity
	\item (4) CSCI 301 Survey of Scripting Languages
	\item (4) CSCI 352 Cyber Defense
\end{checklist}
\end{reqgroup}

\begin{reqgroup}{Information Systems Track (11--12 hours)}
\begin{checklist}
	\item (4) CSCI 419 Database Management
	\item (4) CSCI 495 Systems Analysis and Software Design
	\item (3--4) Any 300/400 level CSCI course that does not duplicate a course in the major.
\end{checklist}
\end{reqgroup}

\begin{reqgroup}{Web Development Track (14 hours)}
\begin{checklist}
	\item (3) ART 216 Visual Communications
	\item (3) ART 221 Digital Image Editing
	\item (4) CSCI 332 Applied Networking
	\item (4) CSCI 334 User-Interface Programming
\end{checklist}
\end{reqgroup}

Notes:%
\begin{enumerate}\footnotesize
	\item Math 110 or higher is a prerequisite and satisfies the Math Liberal Arts Core.
	\item Computer courses should generally be taken in the order listed due to prerequisites.
	\item Courses used in the major cannot be duplicated in the minor.
	\item Graduates must meet residency requirements. The current catalog’s residency requirements are: 36 of the last 46 hours must be earned while attending CSU. Of these, at least 12 hrs must be 300-400 level courses in the major, and at least 6 hrs must be 300-400 level courses in the minor.
	\item In cases of conflict between this checklist and the catalog, the catalog takes precedence.
\end{enumerate}